\documentclass[a4paper,10pt]{article}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{ulem}
\usepackage{fontawesome}

\definecolor{customgreen}{RGB}{38, 130, 63}

\titleformat{\section}{\large\bfseries\color{customgreen}}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[:]

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    urlcolor=black
}

\def\Name{Steven Ye (Zong-Si,Ye)}
\def\Phone{(+886)909926523}
\def\Email{steven.ye1132024@gmail.com}
\def\LinkedIn{https://www.linkedin.com/in/steven-ye1132024/}
\def\GitHub{https://github.com/qaz5823091}

\begin{document}

{\huge \Name} \\ \\
\textcolor{customgreen}{\faPhone} \ \texttt{\Phone} \\
\textcolor{customgreen}{\faEnvelope} \ \href{mailto:\Email}{\underline{\Email}} \\
\textcolor{customgreen}{\faGithub} \ \underline{\href{\GitHub}{github.com/qaz5823091}} \\
\textcolor{customgreen}{\faLinkedin} \ \underline{\href{\LinkedIn}{linkedin.com/in/steven-ye1132024}}

\section*{Professional Summary}
Mobile Engineer with hands-on experience in cross-platform app development using Flutter and native Android. Strong interest in full-stack development and DevOps. Known for self-learning, knowledge sharing, and delivering polished apps from idea to deployment.
\section*{Experience}

\textbf{Mobile Engineer (Flutter) -- MicroProgram}  \hfill Aug. 2024 -- Jun. 2025 \\
Taichung, Taiwan
\begin{itemize}[left=0pt, label={--}]
    \item Developed features for smart bicycle-related projects
    \item Developed and maintained a carbon footprint tracking app project
    \item Maintained the IVM project, which uses Bluetooth to control factory equipment
    \item Improved team development processes for better efficiency and collaboration
    \item Collaborated with the QA team to research and implement mobile app test automation
\end{itemize}

\textbf{Android Internship -- Kdan} \hfill Sep. 2023 -- Jun. 2024 \\
Tainan, Taiwan
\begin{itemize}[left=0pt, label={--}]
    \item Assisted the team in developing products such as a PDF Reader
    \item Maintained and optimized CI/CD pipelines
    \item Ensured development processes complied with ISO 9001 standards
\end{itemize}

\section*{Education}
\textbf{National Chiayi University} \hfill Sep. 2020 -- Jun. 2024 \\
Bachelor of Science in Computer Science \\

GPA: 3.58 / 4.0

\section*{Skills}

\subsection*{Programming}
Dart, Kotlin, JavaScript, Python, C/C++, PHP

\subsection*{Mobile Development}
Flutter - Riverpod / Provider / BLoC, Jetpack Compose, MVVM / Clean Architecture, Firebase, REST APIs, App Publishing (Play Store / App Store)

\subsection*{Collaboration}
Git, GitLab, Postman, UML, UI/UX spec implementation, read / write Technical Docs

\subsection*{DevOps \& CI/CD}
GitLab CI/CD, GitHub Actions, Docker / Docker Compose, Linux (Arch/Ubuntu)

\section*{Languages}
\begin{itemize}[left=0pt, label={--}]
    \item Chinese: Native proficiency
    \item English: Intermediate proficiency with strong reading ; conversational speaking, writing and listening
\end{itemize}


\end{document}